comgen-outline

### 2017-08-10 paper/comgen-paper.Rmd

Figuring out that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect is crucial knowledge in an open-ended world.
Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or just statistically unlikely (e.g., understanding the properties of lightning).
It thus is crucial that language allow us to communicate such *generalizations* to each other.
<!-- The most basic kind of abstract idea is a *generalization* -->

Generalizations are acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010].
Cooperative agents can facilitate inductive learning by supplying helpful data points to the learner [@Csibra2009; @Tomasello1999; @Butler2012].
At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language.
Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
Objects have many properties though; when speakers attach properties to kind-labels (e.g., "Dogs bark"), listeners hear a generalization.

@@

Rational models of communication [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016] have had a lot of recent success in formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014]. 
Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their communicative goals. 
Heretofore, however, the fragments of language under investigation have been limited to utterances that convey information about a specific entity or situation, about the here and now.
Meanwhile, the language of generalizations don't make reference to entities in the world or concrete situations. 
They refers to concepts in the head and have proved tricky to formalize.
<!-- The language of generalization is exceedingly difficult to formalize, however. -->
<!-- The cognitive act of generalization is naturally formalized in Bayesian cognitive models [@Tenenbaum2011]. -->
<!-- Bayesian models showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012]. -->
<!-- Learning from language, however, is more challenging to formalize because of the inherent context-sensitivity of language [@Grice1975; @Clark1996; @Levinson2000]. -->

@@

In this paper, we explore the hypothesis that the core meaning of a generic statement and other language for conveying generalizations is *simple but underspecified*.
We formalize this hypothesis in a probabilistic model of language understanding, and derive predictions for the endorsements of such statements by considering whether or not a speaker would say the generalization to a listener.
We show that this decision depends in systematic ways on the prior knowledge of the listener.
Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
<!-- We relate known measurements on factors regarding generic language to each other via our model. -->
<!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
Our three case studies correspond to generalizations about categories, events, and causes.
We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.

>>>>

Knowing that an object tends to have a property, an entity tends to exhibit a behavior, or a cause tends to produce an effect can be crucial in an open-ended world.
Yet such knowledge can be difficult to acquire: Relevant observations may be costly (e.g., learning that a plant is poisonous) or just statistically unlikely (e.g., understanding the properties of lightning).
It thus is crucial that language allow us to communicate such *generalizations* to each other.

Generalizations are acquired from the world by drawing inductive inferences from observations [@Baldwin1993; @Xu2008; @Dewar2010]. [XXX cite older stuff. eg hume]
Cooperative teachers can facilitate inductive learning by supplying helpful data points to the learner [@Csibra2009; @Tomasello1999; @Butler2012].
At around a child's first birthday, however, the learner gains access to a new, human-unique source of data: language.
Minimally, language fosters generalizations by bringing attention to objects being of the same kind through the use of labeling [e.g., "This is a dog"; @Gelman1986; @Gopnik2000; @Graham2004; @Markman1989; @Schulz2008].
Objects have many properties though; when speakers attach properties to kind-labels (e.g., "Dogs bark"), listeners hear a generalization.

@@

<!-- The language of generalization is exceedingly difficult to formalize, however. -->
<!-- The cognitive act of generalization is naturally formalized in Bayesian cognitive models [@Tenenbaum2011]. -->
<!-- Bayesian models showcase the role of flexibly structured representations [@Kemp2007; @Kemp2008] and assumptions learners can make about the data-generating process [e.g., learning from pedagogical actions; @Shafto2012]. -->
<!-- Learning from language, however, is more challenging to formalize because of the inherent context-sensitivity of language [@Grice1975; @Clark1996; @Levinson2000]. -->

@@

Rational models of communication [@Frank2012; @Goodman2013; @Franke2015; @Goodman2016] have had a lot of recent success in formalizing complex linguistic phenomena ranging from politeness [@Yoon2016] and hyperbole [@Kao2014] to metaphor [@Kao2014] and vagueness [@Lassiter2013; @Qing2014]. 
Such models of rational communication describe the inferences listeners can draw from language, and the utterances speakers should say given their communicative goals. 
Heretofore, however, the fragments of language under investigation have been limited to utterances that convey information about a specific entity or situation, about the here and now.
Meanwhile, the language of generalizations don't make reference to entities in the world or concrete situations. 
They refers to concepts in the head and have proved tricky to formalize.

In this paper, we explore the hypothesis that the core meaning of a generic statement and other language for conveying generalizations is *simple but underspecified*.
We formalize this hypothesis in a probabilistic model of language understanding, and derive predictions for the endorsements of such statements by considering whether or not a speaker would say the generalization to a listener.
We show that this decision depends in systematic ways on the prior knowledge of the listener.

Across three distinct case studies, we both measure and manipulate prior knowledge, showing that it is strongly and causally related to the endorsement of generalizations in the ways predicted by our model.
<!-- We relate known measurements on factors regarding generic language to each other via our model. -->
<!-- We then go on to manipulate the relevant factors, showing they are causally related via our model to generic endorsement and interpretation.  -->
Our three case studies correspond to generalizations about categories, events, and causes.
We show that in each domain, our general theoretical framework explains endorsements about generalizations conveyed in language, while simpler models fall short.
